Ensemble Methods for Robust Feature Selection

### 2016-08-02 paper/paper.tex
combination_accuracy figure

\usepackage{jmlr2e}
\usepackage{amsmath}
\usepackage{enumitem}

@@

The second feature selection is RELIEFF \citep{kononenko1997overcoming}. For each sample $x_i$ the k nearest neighboring samples, using the $L_1$ norm, belonging the same class $\{\textrm{Near-hit}_{i, j}\}_{j=1..k}$ and the ones of the opposite class $\{\textrm{Near-miss}_{i, j}\}_{j=1..k}$ are selected. Then the difference is taken to update the weight vector representing how well each feature distinguishes samples of the two classes, as can be seen in equation \ref{eq:relief}. In all the experiments k was set to 5, which, empirically, gives satisfactory results. 
\\
?? \\
In the standard case of RELIEF for comparisment the euclidean distance is used for numerical values. This inherits the
assumption that features which are nearer to each other are also more similar, which should not be correct in each application
area.\\
??
\begin{equation}
  \label{eq:relief}
  W_i = W_i - \frac{1}{k}\sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \frac{1}{k}\sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
\end{equation}

@@

\subsection{Data Sets}
Datasets are taken from the NIPS 2003 challenge \cite{NIPS}. However, due to computation power constraints, not the whole dataset is always used. Additionally the colon data set \cite{alon1999broad} is used. Finally artificial data is also generated, since it is possible to control which features are meaningful.

@@

\subsubsection{Different combinations of feature selectors}
The presented ensemble methods were used with all possible combinations of feature selectors. For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset. While the accuracy does not change considerably with the different combinations, the robustness is heavily affected by the presence or not of the feature selector Lasso as can be seen in the figure \ref{fig:combination_robustness}. This is due to the low robustness of the feature selector Lasso itself. On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.

\begin{figure}
\centering \includegraphics[]{images/Robustness_of_the_different_combinations.pdf}
\caption{Robustness of the different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
\label{fig:combination_robustness}
\end{figure}

>>>>

\usepackage{jmlr2e}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{subcaption}

@@

The second feature selection is RELIEFF \citep{kononenko1997overcoming}. For each sample $x_i$ the k nearest neighboring samples, using the $L_1$ norm, belonging the same class $\{\textrm{Near-hit}_{i, j}\}_{j=1..k}$ and the ones of the opposite class $\{\textrm{Near-miss}_{i, j}\}_{j=1..k}$ are selected. Then the difference is taken to update the weight vector representing how well each feature distinguishes samples of the two classes, as can be seen in equation \ref{eq:relief}. In all the experiments k was set to 5, which, empirically, gives satisfactory results.
\begin{equation}
  \label{eq:relief}
  W_i = W_i - \frac{1}{k}\sum_{j=1}^{k}|x_i - \textrm{Near-hit}_{i,j}| + \frac{1}{k}\sum_{j=1}^{k} |x_i - \textrm{Near-miss}_{i,j}|
\end{equation}

@@

\subsection{Data Sets}
Datasets are taken from the NIPS 2003 challenge (\cite{NIPS}). However, due to computation power constraints, not the whole dataset is always used. Additionally the colon data set (\cite{alon1999broad}) is used. Finally artificial data is also generated, since it is possible to control which features are meaningful.

@@

\subsubsection{Different combinations of feature selectors}
The presented ensemble methods were used with all possible combinations of feature selectors. For each combination, the average of the results was taken, and the error plot corresponds to the mean of the standard deviation of each ensemble method and each dataset. While the accuracy does not change considerably with the different combinations, see figure \ref{fig:combination_accuracy}, the robustness is heavily affected by the presence or not of the feature selector Lasso as presented in the figure \ref{fig:combination_robustness}. This is due to the low robustness of the feature selector Lasso itself. On the opposite SU and RELIEFF being quite robust, their combination, with or without SVM, are the most robust.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Accuracy_of_the_different_combinations.pdf}
  \caption{Accuracy}
  \label{fig:combination_accuracy}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=1.07\textwidth]{images/Robustness_of_the_different_combinations.pdf}
  \caption{Robustness}
  \label{fig:combination_robustness}
\end{subfigure}
\caption{Different combination of feature selectors (RLF and LSO corresponds respectively to RELIEFF and Lasso)}
\label{fig:combination_results}
\end{figure}
